Simulation Results

### 2020-05-04 Simulation Results/Simulation Results.Rmd
ppp updates

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
library(tidyverse); options(tibble.width = Inf)
library(magrittr)
library(here)
```

@@

  # expression_string <- combined_results$expression[[7]]
  # expression_string
  get_method_name <- function(expression_string) {
    string <- as.character(expression_string)[1]
    string
    if (string == "run.jags") {
      method <- "JAGS"
    } else if (string == "bugs") {
      method <- "OpenBUGS"
    } else if (string == "nimbleMCMC") {
      method <- "Nimble"
    } else if (string == "stan") {
      method <- "STAN"
    } else if (string == "mcmc") {
      method <- "Greta"
    } else if (string == "stan_model") {
      method <- "STAN Compile"
    }
    method
  }

@@

bench_results_indiv <- bench_results_indiv %>% 
  filter(!(method == "STAN Compile" & time < 5))

saveRDS(bench_results_indiv, file = "bench_results_indiv.RDS")
```

@@

```{r}
bench_results_indiv <- readRDS("bench_results_indiv.RDS")

bench_results_indiv %>%
  ggplot(aes(time, color = method)) +
  geom_boxplot() +
  coord_flip() +
  xlim(0,90)

bench_results_indiv %>%
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  # xlim(0,100) +
  facet_wrap(vars(method))

bench_results_indiv %>%
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  xlim(0,100) +
  facet_wrap(vars(method))

@@

files <- normal_normal_acc_files
model_name <- "poisson_gamma"

@@

@@

time_results %>% 
  pivot_longer(
    cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    names_to = "method",
    values_to = "TVD"
  ) %>% 
  ggplot(aes(TVD)) + 
    geom_histogram() + 
    facet_wrap(facets = "method")

time_results %>% 
  pivot_longer(
    cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    names_to = "method",
    values_to = "TVD"
  ) %>% 
  ggplot(aes(TVD)) + 
    geom_boxplot(aes(color = method)) + 
    coord_flip() + 
    xlim(0,0.25)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
library(tidyverse); options(tibble.width = Inf); theme_set(theme_bw())
library(magrittr)
library(here)
```

@@

  # expression_string <- combined_results$expression[[7]]
  # expression_string
  get_method_name <- function(expression_string) {
    string <- as.character(expression_string)[1]
    string
    if (string == "run.jags") {
      method <- "JAGS"
    } else if (string == "bugs") {
      method <- "OpenBUGS"
    } else if (string == "nimbleMCMC") {
      method <- "Nimble"
    } else if (string == "stan") {
      method <- "Stan"
    } else if (string == "mcmc") {
      method <- "Greta"
    } else if (string == "stan_model") {
      method <- "Stan Compile"
    }
    method
  }

@@

bench_results_indiv <- bench_results_indiv %>% 
  filter(!(method == "Stan Compile" & time < 5))

# saveRDS(bench_results_indiv, file = "bench_results_indiv.RDS")
# saveRDS(bench_results_indiv, file = "bench_results_indiv2.RDS")
```

@@

```{r}
bench_results_indiv <- readRDS("bench_results_indiv2.RDS")

bench_results_indiv %>%
  ggplot(aes(x = method, y = time)) +
  geom_boxplot(aes(color = method), coef = 2, outlier.size = 0.75) +
  # geom_boxplot(aes(color = method)) +
  # coord_flip() +
  ylim(0,90) +
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan", "Nimble", "Greta", "Stan Compile")) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5)) + 
  xlab("Implementation") + 
  ylab("Completion Time") + 
  ggtitle("Implementation Completion Time Boxplots")

bench_results_indiv %>%
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  # xlim(0,100) +
  facet_wrap(vars(method)) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("Implementation Completion Time Histograms") + 
  xlab("Completion Time") + 
  ylab("Count Density")

bench_results_indiv %>%
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  xlim(0,100) +
  facet_wrap(vars(method)) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("Implementation Completion Time Histograms") + 
  xlab("Completion Time") + 
  ylab("Count Density")

bench_results_indiv %>%
  filter(method %in% c("JAGS", "Nimble", "OpenBUGS", "Stan")) %>% 
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  # xlim(0,100) +
  facet_wrap(vars(method)) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("Implementation Completion Time Histograms") + 
  xlab("Completion Time") + 
  ylab("Count Density")

@@

files <- poisson_gamma_acc_files
model_name <- "poisson_gamma"

@@

  stan_mean <- combined_results$stan_dist %>% mean()

  combined_results <- combined_results %>% 
    mutate(JAGS = jags_dist / stan_mean, 
           OpenBUGS = bugs_dist / stan_mean, 
           Stan = stan_dist / stan_mean, 
           Nimble = nimble_dist / stan_mean, 
           Greta = greta_dist / stan_mean
           )

@@

time_results %>% 
  pivot_longer(
    # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta), 
    names_to = "method",
    values_to = "TVD_Ratio"
  ) %>% 
  ggplot(aes(TVD_Ratio)) + 
    geom_histogram(aes(fill = method)) + 
    facet_wrap(facets = "method") + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("Implementation TVD Accuracy Histograms") + 
  xlab("Implementation") + 
  ylab("TVD Ratio")

time_results %>% 
  pivot_longer(
    # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta), 
    names_to = "method",
    values_to = "TVD_Ratio"
  ) %>% 
  ggplot(aes(x = method, y = TVD_Ratio)) + 
    geom_boxplot(aes(color = method)) + 
  ggtitle("Implementation TVD Accuracy Boxplots") + 
  xlab("Implementation") + 
  ylab("TVD Ratio") + 
  scale_x_discrete(limits = c("OpenBUGS", "JAGS", "Nimble", "Stan", "Greta")) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5))
